Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-07 providence/sections/intro.tex
.

A ballot polling audit begins when a {\em round} \cite{usenix_minerva} of multiple randomly-chosen ballots is drawn. A risk measure is then computed to determine whether (a) the audit ends in success (the election outcome is declared correct) or (b) another round should be drawn. It is possible to design audits which output a third determination, (c) the audit proceeds to a full manual hand count. To allow maximum flexibility for election officials to make this logistically involved decision, this third output is generally not included. Election officials would typically decide to perform a full manual hand count if the audit does not stop in spite of drawing a large number of ballots, typically over multiple rounds. 
Ballot polling audits have been used in a number of US state pilots (California, Georgia, Indiana, Michigan, Ohio, Pennsylvania, Virginia and elsewhere) and in real statewide audits (Georgia, Virgina) \cite{vv_audits} as well as in audits of smaller jurisdictions, such as Montgomery County, Ohio \cite{usenix_minerva}.

>>>>

A ballot polling audit begins with choosing a first {\em round} \cite{usenix_minerva} size, the number of ballots sampled before first checking the stopping condition.
Ballots on the ballot manifest are then sampled uniformly at random using a pseudorandom number generator typically seeded by a natural source of randomness like rolling dice.
The physical ballots are then found and manually interpreted, recording the manual interpretations.
Based on the manual interpretations, a risk measure is computed to determine whether (a) the audit ends in success (the election outcome is declared correct) or (b) another round should be drawn. It is possible to design audits which output a third determination, (c) the audit proceeds to a full manual hand count. To allow maximum flexibility for election officials to make this logistically involved decision, this third output is generally not included. Election officials would typically decide to perform a full manual hand count if the audit does not stop in spite of drawing a large number of ballots, typically over multiple rounds.

Ballot polling audits have been used in a number of US state pilots (California, Georgia, Indiana, Michigan, Ohio, Pennsylvania, Virginia and elsewhere) and in real statewide audits (Georgia, Virgina) \cite{vv_audits} as well as in audits of smaller jurisdictions, such as Montgomery County, Ohio \cite{usenix_minerva}.
